%______________________________________________________________________________________________________________________
% @brief    
\documentclass[margin,line]{resume}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{nth}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large{Agnieszka Borowska} \hfill \small{02 April 2018} \hspace{2.8cm}} 
\begin{resume}
%__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    Vrije Universiteit Amsterdam \hfill  E-mail: \url{a.borowska@vu.nl} \\
    Department of Econometrics and Operational Research \hfill Website: \url{aborowska.github.io}\\ \vspace{0mm}%
    De Boelelaan 1105  \hfill Mobile: +31 6 16 028 686\\
    1081HV Amsterdam\\ \vspace{-4.5mm}%
%__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    
    Bayesian Methods, State Space Models, Sequential Monte Carlo, Simulation Techniques, Rare \\ Events Estimation
   %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{VU Amsterdam},  The Netherlands, \hfill Sep. 2015 -- Summer 2018 (expected)\\
	Ph.D. in Econometrics,\\ 
    Supervisors: Prof. Siem Jan Koopman and Dr Lennart. Hoogerheide

\vspace{-1mm}

    \textbf{University of Edinburgh},  UK, \hfill Apr. 2017 -- Jun. 2017\\
	Postgraduate Research Visit at the School of Mathematics,\\ 
    Host Supervisor: Prof. Ruth King

\vspace{-1mm}

    \textbf{Tinbergen Institute} and \textbf{VU Amsterdam}, The Netherlands  \hfill Sep. 2013 -- Aug. 2015 	\\
	M.Phil., \textit{major:} Econometrics, \textit{minor:} Macroeconomics 

\vspace{-1mm}

	\textbf{University of Warsaw}, Poland  \hfill Oct. 2009 -- Sep. 2013 	
	\vspace{1mm}\\
	Faculty of Mathematics, Informatics and Mechanics \\B.Sc. in Mathematics, \textit{minor:} Probability Theory 
    
\vspace{-1mm}

	\textbf{University of G{\"o}ttingen}, Germany   \hfill Sep. 2010 -- Feb. 2011	\\
    Faculty of Economics and Business Administration \\M.Sc. programme, exchange within the Erasmus Programme

\vspace{-1mm}

	\textbf{Warsaw School of Economics}, Poland   \hfill Oct. 2009 -- Jan. 2012\\
	M.Sc. in Economics, \textit{major:} Macroeconomic Analysis

\vspace{-1mm}

 	\textbf{Warsaw School of Economics}, Poland  \hfill Oct. 2006 --  Jul. 2009\\
   	B.Sc. in Economics, \textit{major:} Macroeconomic Analysis,\\ 
    \textit{minor:} Computational and Optimisation Methods in Decision Making\\
    
\vspace{-4mm}
\section{\mysidestyle Publication}
	\textit{Bayesian Dynamic Modeling of High-Frequency Integer Price Changes},\\
	with Istv\'{a}n Barra  and Siem Jan Koopman,\\
	forthcoming in \textit{Journal of Financial Econometrics}, 2018  \vspace{-5mm} \\ 
	
\section{\mysidestyle Under revision}
	\textit{Time-varying Combinations of Bayesian Dynamic Models and Equity Momentum Strategies},\\
	with Nalan Ba\c{s}t\"{u}rk, Stefano Grassi, Lennart Hoogerheide and Herman K. van Dijk,\\
	revision for \textit{Journal of Econometrics} \vspace{-5mm} \\ 
 	
\section{\mysidestyle Ongoing \\Research } 
   	\textit{Bayesian Risk Evaluation for Long Horizons},\\ 
   	\textbf{Job Market Paper} \\ 
   	available at \href{https://aborowska.github.io/research/A.Borowska\%20-\%20Bayesian\%20Risk\%20Evaluation\%20for\%20Long\%20Horizons.pdf}{https://aborowska.github.io/research/}  \vspace{1mm} \\
   	\textit{Semi-Complete Data Augmentation},\\ 
    with Ruth King \vspace{1mm} \\   
   	\textit{Partially Censored Posterior},\\ 
    with Lennart Hoogerheide and Siem Jan Koopman \\   	
   	available at \href{https://aborowska.github.io/research/Borowska,\%20Hoogerheide,\%20Koopman\%20-\%20Partially\%20censored\%20posterior\%20for\%20accurate\%20left\%20tail\%20density\%20prediction.pdf}{https://aborowska.github.io/research/} \vspace{1mm}\\
   	\textit{Bayesian Risk Evaluation for State-Space Models},\\ 
    with Lennart Hoogerheide and Siem Jan Koopman\vspace{1mm} \\  
      
\vspace{-4mm}





%__________________________________________________________________________________________________________________
 \newpage	

\section{\mysidestyle Conference \\and Seminar \\Presentations} 
	\textbf{\nth{1} Bayes Comp}, Barcelona, Spain \hfill 26-- 28 Mar. 2018 \vspace{1mm} \\
	\textbf{\nth{10} International Conference of the ERCIM WG on Computational and}\\
	\textbf{Methodological Statistics}, London, UK\hfill 16-- 18 Dec. 2017 \vspace{1mm} \\ 	
	\textbf{\nth{8} European Seminar on Bayesian Econometrics},\\
	 Maastricht, The Netherlands\hfill 26-- 27 Oct. 2017 \vspace{1mm} \\ 
	\textbf{Sequential Monte Carlo Workshop 2017}, Uppsala, Sweden\hfill 30 Aug. -- 1 Sep. 2017 \vspace{1mm} \\ 
	%\textit{Time-varying Combinations of Bayesian Dynamic Models and Equity Momentum Strategies} \vspace{1mm} \\      
	\textbf{\nth{1} International Conference on Econometrics and Statistics},\\ Hong Kong \hfill 15--17 Jun. 2017 \vspace{1mm} \\ 
	%\textit{Partially Censored Posterior for Accurate Left Tail Density Prediction} \vspace{1mm} \\      
    \textbf{Statistics Seminar Series of the School of Mathematics},\\ Edinburgh, UK \hfill 19 May 2017 \vspace{1mm} \\ 
    \textbf{\nth{10} International Conference on Computational and Financial Econometrics},\\ Seville, Spain\hfill 9--11 Dec. 2016\\ 
%	\textit{Bayesian Risk Evaluation for Long Horizons} \vspace{1mm} \\ 
	\textbf{\nth{3} Bayesian Young Statisticians Meeting}, Florence, Italy \hfill 20--21 Jun. 2016\\ 
	%\textit{Bayesian Risk Evaluation in State Space Models using Importance Sampling} [poster] \vspace{1mm} \\  
    \textbf{\nth{11} Netherlands Econometric Study Group Meeting}, Leuven, Belgium \hfill 17--18 Jun. 2016\\ 
%	\textit{Bayesian Risk Evaluation for Long Horizons} \vspace{1mm} \\  
     \textbf{TI Ph.D. Lunch Seminar}, Amsterdam, The Netherlands \hfill 24 May 2016\\ 
 % \textit{Bayesian Risk Evaluation in State Space Models using Importance Sampling} \\  
	\textbf{Econometrics Brown Bag Seminar}, Amsterdam, The Netherlands \hfill 21 Jan. 2016\\ 
  %\textit{Bayesian Risk Evaluation for Long Horizons} \\  

\vspace{-3mm}


  
   \section{\mysidestyle Scholarships}	
   	\textbf{SMC2017 scholarship to attend the workshop and the intensive course}\\ SMC2017 organizing committee, 15,000 SEK. \hfill Aug. 2017 \vspace{1.5mm} \\   
   	\textbf{Tinbergen Institute merit-based scholarship}\\ Tinbergen Institute, full scholarship, first and second year, 30,000 EUR \hfill Sep. 2013 -- Aug. 2015\vspace{1.5mm} \\   
       \textbf{Student Exchange Scholarship}\\  Warsaw School of Economics, the LLP Erasmus \hfill Sep. 2010 -- Feb. 2011\vspace{1.5mm} \\
       \textbf{Scholarship for excellent academic achievements}\\ Warsaw School of Economics \hfill Oct. 2007 -- Sep. 2010 


    % Computer Skills
   \section{\mysidestyle Computer\\ Skills} 
   Strong experience in MATLAB, Fortran, R   \vspace{1mm}\\
   Experience with Python, C, PHP, Visual Basic, SQL, BUGS/JAGS \vspace{1mm}\\
	Familiarity with EViews, Stata, SPSS \vspace{1mm} \\
 %   Databases:	EcoWin, Reuters \vspace{1mm}\\
	Other: \LaTeX, Linux, GitHub, SVN  

    % Foreign Languages
   \section{\mysidestyle Foreign Languages}  
	Polish (native), English (fluent),  German (advanced),    \\
    Russian (intermediate),  French (basic),  Dutch (basic)

 
    
\section{\mysidestyle Referees} 

 \textbf{Prof. Siem Jan Koopman} \\    
 The Department of Econometrics \\
 Vrije Universiteit Amsterdam, e-mail: \url{s.j.koopman@vu.nl}

 \textbf{Dr Lennart Hoogerheide} \\  
 The Department of Econometrics \\  
 Vrije Universiteit Amsterdam, e-mail: \url{l.f.hoogerheide@vu.nl}

 \textbf{Prof. Ruth King} \\  
 The School of Mathematics,\\  
 The University of Edinburgh, e-mail: \url{ruth.king@ed.ac.uk}
 
 \textbf{Prof. Herman K. van Dijk} \\  
 Econometric Institute,\\  
 Erasmus University Rotterdam, e-mail: \url{hkvandijk@ese.eur.nl }
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}