%______________________________________________________________________________________________________________________
% @brief    
\documentclass[margin,line]{resume}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{nth}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large{Agnieszka Borowska} \hfill \small{31 March 2019} \hspace{2.8cm}} 
\begin{resume}
%__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
%    Vrije Universiteit Amsterdam \hfill  E-mail: \url{a.borowska@vu.nl} \\
%    Department of Econometrics and Operational Research \hfill Website: \url{aborowska.github.io}\\ \vspace{0mm}%
%    De Boelelaan 1105  \hfill Mobile: +31 6 16 028 686\\
%    1081HV Amsterdam\\ \vspace{-4.5mm}%
    University of Glasgow\hfill  E-mail: \url{Agnieszka.Borowska@glasgow.ac.uk} \\
    School of Mathematics and Statistics \hfill Website: \url{aborowska.github.io}\\ \vspace{0mm}%
    University Place \\
    Glasgow G12 8QQ\\ \vspace{-4.5mm}%    
%__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    
    Bayesian Methods, State Space Models, Sequential Monte Carlo, Simulation Techniques, Rare \\ Events Estimation

%__________________________________________________________________________________________________________________
 
    % Education
    \section{\mysidestyle Current Position}
    \textbf{University of Glasgow},  UK, \hfill from May 2018\\
	Postdoctoral researcher in Statistics (with Prof. Dirk Husmeier),\\ 
    Position within the \href{http://softmech.org/}{SofTMech Centre} (an EPSRC centre for Multiscale Soft Tissue Mechanics)

\vspace{-1mm}    
%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{VU Amsterdam},  The Netherlands, \hfill Sep. 2015 -- Spring 2019 (expected)\\
	Ph.D. in Econometrics,\\ 
    Supervisors: Prof. Siem Jan Koopman and Dr Lennart. Hoogerheide

\vspace{-1mm}

    \textbf{University of Edinburgh},  UK, \hfill Apr. 2017 -- Jun. 2017\\
	Postgraduate Research Visit at the School of Mathematics,\\ 
    Host Supervisor: Prof. Ruth King

\vspace{-1mm}

    \textbf{Tinbergen Institute} and \textbf{VU Amsterdam}, The Netherlands  \hfill Sep. 2013 -- Aug. 2015 	\\
	M.Phil., \textit{major:} Econometrics, \textit{minor:} Macroeconomics 

\vspace{-1mm}

	\textbf{University of Warsaw}, Poland  \hfill Oct. 2009 -- Sep. 2013 	
	\vspace{1mm}\\
	Faculty of Mathematics, Informatics and Mechanics \\B.Sc. in Mathematics, \textit{minor:} Probability Theory 
    
\vspace{-1mm}

	\textbf{University of G{\"o}ttingen}, Germany   \hfill Sep. 2010 -- Feb. 2011	\\
    Faculty of Economics and Business Administration \\M.Sc. programme, exchange within the Erasmus Programme

\vspace{-1mm}

	\textbf{Warsaw School of Economics}, Poland   \hfill Oct. 2009 -- Jan. 2012\\
	M.Sc. in Economics, \textit{major:} Macroeconomic Analysis

\vspace{-1mm}

 	\textbf{Warsaw School of Economics}, Poland  \hfill Oct. 2006 --  Jul. 2009\\
   	B.Sc. in Economics, \textit{major:} Macroeconomic Analysis,\\ 
    \textit{minor:} Computational and Optimisation Methods in Decision Making\\
    
\vspace{-4mm}
\section{\mysidestyle Publications}
\textit{Time-varying Combinations of Bayesian Dynamic Models and Equity Momentum Strategies},\\
	with Nalan Ba\c{s}t\"{u}rk, Stefano Grassi, Lennart Hoogerheide and Herman K. van Dijk,\\
	\textit{Journal of Econometrics}, 2018 \vspace{1mm} \\
\textit{Bayesian Dynamic Modeling of High-Frequency Integer Price Changes},\\
	with Istv\'{a}n Barra  and Siem Jan Koopman,\\
	\textit{Journal of Financial Econometrics}, 2018  \vspace{-5mm} \\ 
	 	
\section{\mysidestyle Submitted and under revision}	
\textit{Partially Censored Posterior for Robust and Efficient Risk Evaluation},\\
	with Lennart Hoogerheide, Siem Jan Koopman and Herman K. van Dijk,\\
	revision for \textit{Journal of Econometrics} \vspace{1mm}\\ 
\textit{Bayesian Risk Forecasting for Long Horizons},\\
	with Lennart Hoogerheide and Siem Jan Koopman, \vspace{-5mm} \\ 
		 	
\section{\mysidestyle Ongoing \\Research } 
   	\textit{Gaussian Processes and ABC for Statistical Inference in Cell Migration SDE Systems},\\ 
    with Diana Giurghita and Dirk Husmeier\vspace{1mm} \\
   	\textit{Bayesian Optimisation for Left Ventricle Biomechanical Models},\\ 
    with Dirk Husmeier, Hao Gao and Xiaoyu Luo \vspace{1mm} \\   	
   	\textit{Semi-Complete Data Augmentation},\\ 
    with Ruth King \vspace{1mm} \\   
   	\textit{Bayesian Risk Evaluation for State-Space Models},\\ 
    with Lennart Hoogerheide and Siem Jan Koopman\vspace{1mm} \\  
      
\vspace{-4mm}





%__________________________________________________________________________________________________________________
 \newpage	

\section{\mysidestyle Conference \\and Seminar \\Presentations} 
	\textbf{\nth{39} International Symposium on Forecasting} (scheduled),\\
	Thessaloniki, Greece \hfill 16--19 Jun. 2018 \vspace{1mm} \\	
	\textbf{Workshop on Uncertainty Quantification for Cardiac Models} (scheduled),\\
	Cambridge, UK \hfill 5--7 Jun. 2019 \vspace{1mm} \\		
	\textbf{Cside 2018 Conference}, Glasgow, UK \hfill 26 Nov. 2018 \vspace{1mm} \\
	\textbf{\nth{2} Joint Liverpool-Glasgow Maths Healthcare Centre Meeting},\\
	Liverpool, UK \hfill 30 Aug. 2018 \vspace{1mm} \\	
	\textbf{\nth{4} Bayesian Young Statisticians Meeting}, Warwick, UK \hfill 02 -- 03 Jul. 2018 \vspace{1mm} \\
	\textbf{\nth{1} Bayes Comp}, Barcelona, Spain \hfill 26-- 28 Mar. 2018 \vspace{1mm} \\
	\textbf{\nth{10} International Conference of the ERCIM WG on Computational and}\\
	\textbf{Methodological Statistics}, London, UK\hfill 16-- 18 Dec. 2017 \vspace{1mm} \\ 	
	\textbf{\nth{8} European Seminar on Bayesian Econometrics},\\
	 Maastricht, The Netherlands\hfill 26--27 Oct. 2017 \vspace{1mm} \\ 
	\textbf{Sequential Monte Carlo Workshop 2017}, Uppsala, Sweden\hfill 30 Aug. -- 1 Sep. 2017 \vspace{1mm} \\ 
	%\textit{Time-varying Combinations of Bayesian Dynamic Models and Equity Momentum Strategies} \vspace{1mm} \\      
	\textbf{\nth{1} International Conference on Econometrics and Statistics},\\ Hong Kong \hfill 15--17 Jun. 2017 \vspace{1mm} \\ 
	%\textit{Partially Censored Posterior for Accurate Left Tail Density Prediction} \vspace{1mm} \\      
    \textbf{Statistics Seminar Series of the School of Mathematics},\\ Edinburgh, UK \hfill 19 May 2017 \vspace{1mm} \\ 
    \textbf{\nth{10} International Conference on Computational and Financial Econometrics},\\ Seville, Spain\hfill 9--11 Dec. 2016\\ 
%	\textit{Bayesian Risk Evaluation for Long Horizons} \vspace{1mm} \\ 
	\textbf{\nth{3} Bayesian Young Statisticians Meeting}, Florence, Italy \hfill 20--21 Jun. 2016\\ 
	%\textit{Bayesian Risk Evaluation in State Space Models using Importance Sampling} [poster] \vspace{1mm} \\  
    \textbf{\nth{11} Netherlands Econometric Study Group Meeting}, Leuven, Belgium \hfill 17--18 Jun. 2016\\ 
%	\textit{Bayesian Risk Evaluation for Long Horizons} \vspace{1mm} \\  
     \textbf{TI Ph.D. Lunch Seminar}, Amsterdam, The Netherlands \hfill 24 May 2016\\ 
 % \textit{Bayesian Risk Evaluation in State Space Models using Importance Sampling} \\  
	\textbf{Econometrics Brown Bag Seminar}, Amsterdam, The Netherlands \hfill 21 Jan. 2016\\ 
  %\textit{Bayesian Risk Evaluation for Long Horizons} \\  

\vspace{-3mm}


 
 \section{\mysidestyle Teaching Experience}
    \textbf{University of Glasgow}, UK\\ 
    \textit{Honours and MSc Projects supervision} (Statistics)  \hfill 2018/2019 \\
    Co-supervision with Dirk Husmeier \vspace{1mm}\\  	
    \textbf{VU Amsterdam}, the Netherlands \\ 
    \textit{Econometrics II} (B.Sc. course)  \hfill Feb. -- Mar. 2017 \\
    Teaching Assistant of Lennart Hoogerheide  \vspace{1mm}\\  	
    \textit{Business Mathematics} (B.Sc. course, evaluation: 3.8/5)  \hfill Sep. -- Oct. 2016 \vspace{1mm}\\ 
    \textit{Business Statistics} (B.Sc. course, evaluation: 4.1/5)  \hfill Feb. -- Mar. 2016 \vspace{1.5mm}\\
   	\textbf{Tinbergen Institute}, Amsterdam, the Netherlands \\
    \textit{Advanced Econometrics II} (M.Phil. course, evaluation: 4.1/5) \hfill Jan. -- Feb. 2015\\
      Teaching Assistant of Kees Jan van Garderen  \vspace{1mm} \\
	\textit{Measure Theory and Stochastic Processes} (M.Phil. course, evaluation: 4.2/5) \hfill Sep. -- Oct. 2014\\
     Teaching Assistant of Peter J. C. Spreij   

 % Professional Experience 
    \section{\mysidestyle Professional and Research Experience}
    \textbf{University of Warsaw}, Poland \vspace{0mm}\\
    \textsl{Researcher} \hfill Feb. 2012 -- Sep. 2014\\
Pension system reform modelling within the OLG framework under time inconsistency; welfare analysis of various fiscal closures; numerical model solving in Fortran; paper writing and editing.\vspace{1.5mm} \\
    \textbf{Civil Development Forum}, Warsaw, Poland \\
    \textsl{Internship in the Analytical Department} \hfill Jul. 2010\\
Analysis of the privatisation process in Poland; comparison of fiscal policy rules in selected EU countries; development of a database on fiscal stability reforms in the EU.\vspace{1.5mm} \\
	\textbf{National Bank of Poland}, Warsaw, Poland \\
    \textsl{Internship in the Economics Institute, Monetary Policy Strategy Bureau} \hfill Aug. 2009\\
Comparison and evaluation of the communication tools and institutional solutions implemented in selected central banks worldwide.  


\newpage	        
  
   \section{\mysidestyle Additional\\ Courses \\and Trainings} 
	\textbf{Forecasting Summer School} (scheduled)\\
        Thessaloniki, Greece\hfill Jun. 2019\\
        Probabilistic forecasting (scoring rules, combining predictive distributions)\vspace{1.5mm} \\	
	\textbf{Scalable Bayesian Inference}\\
        Edinburgh, UK\hfill Jun. 2018\\
        Scalable algorithms for large datasets (embarrassingly parallel MCMC, approximate MCMC),\\ scalable Bayesian methods for very high-dimensional data analysis\vspace{1.5mm} \\	
	\textbf{Workshop on Machine Learning Models and Methods for Econometricians}\\
        Maastricht, The Netherlands\hfill Oct. 2017\\
        Gaussian processes, distributed and subsampling MCMC, variational Bayes,  deep ;earning\vspace{1.5mm} \\	
	\textbf{Intensive PhD level course on Sequential Monte Carlo Methods}\\
        Uppsala University, Sweden\hfill Aug. 2017\\
        Particle MCMC, high-dimensional filtering, SMC for probabilistic graphical models and probabilistic programming\vspace{1.5mm} \\   
	\textbf{Reading Group on Bayesian Nonparametrics}\\
        University of Edinburgh, UK \hfill May -- Jun. 2017\\
        Introduction to Dirichlet process and their mixtures, Bayesian nonparamteric regression\vspace{1.5mm} \\
	\textbf{Course on High Performance Computing}\\
        VU Amsterdam, The Netherlands \hfill Oct. 2016\\
        Basics of Unix and cluster computing,  Hadoop and data analytics, GPU programming, HPC cloud\vspace{1.5mm} \\
%     \textbf{TI Econometrics Lectures 2015}, Rotterdam, The Netherlands \hfill \textbf{June 2015}\\ 
%   \textit{Structural Modelling of Economic Time Series} \\ Participation in the lecture 
%   
%        \textbf{TI Economics Lectures 2015}, Amsterdam, The Netherlands \hfill \textbf{May 2015}\\ 
% \textit{New Style Central Banking}\\
% Participation in the lecture
%
%     \textbf{TI Econometrics Lectures 2014}, Rotterdam, The Netherlands \hfill \textbf{June 2014}\\ 
%   \textit{The Econometric Analysis of Recurrent Events in Economics and Finance} \\ Participation in the lecture (final grade: 9)
%   
%        \textbf{TI Economics Lectures 2014}, Amsterdam, The Netherlands \hfill \textbf{June 2014}\\ 
% \textit{Markets with Asymmetric Information}\\
% Participation in the lecture (final grade: 8)
%   
%        \textbf{18th International Conference on Macroeconomic Analysis and International Finance} University of Crete, Rethymno, Greece \hfill \textbf{May 2014} \\ 
%   Participation in the conference as a co-author of a presented paper
%
%        \textbf{Current Trends in Macroeconomic and Finance Research},\\  National Bank of Poland, Warsaw, Poland  \hfill \textbf{July 2012}\\ 
%  Participation in the economics workshop
%
        \textbf{Summer School in Applied Macroeconomics}\\
        University of Salento, Lecce, Italy \hfill Jul. 2012\\
        Programming in Matlab,  VAR for monetary policy, state space models and the Kalman Filter%
%23 - 27 July 2012
%        \textbf{DSGE and beyond –- expanding the paradigm in monetary policy research?}\\  National Bank of Poland, Warsaw, Poland \hfill \textbf{September 2011}\\ 
%  Participation in the conference
 
%        \textbf{Introduction to Stata}, University of G{\"o}ttingen, Germany \hfill \textbf{December 2010} 	\\
%        Block course covering basic commands, data management, graphs, data manipulation, descriptive statistics, regression analysis and basic programming in Stata.

%        \textbf{SQL course}, University of G{\"o}ttingen,  Germany \hfill \textbf{November 2010} \\ 
% Principles of  relational databases  and SQL queries.


%  \newpage
%   __________________________________________________________________________________________________________________
% \newpage	
 

	% Scholarships

   \section{\mysidestyle Scholarships \\and Awards}	
   	\textbf{IIF travel award grant to attend ISF 2019 and the forecasting summer school} \\
   	International Institute of Forecasters, 1660 USD \hfill Mar. 2019 \vspace{1.5mm} \\ 
   	\textbf{Cside 2018 winners' prize} \\
   	(Model 3 and Additional Challenge), 250 GBP \hfill Nov. 2018 \vspace{1.5mm} \\ 
   	\textbf{ISBA travel award to attend BAYSM 2018}\\ BAYSM 2018 organizing committee, 400 USD \hfill Apr. 2018 \vspace{1.5mm} \\ 
   	\textbf{SMC2017 scholarship to attend the workshop and the intensive course}\\ SMC2017 organizing committee, 15,000 SEK \hfill Aug. 2017 \vspace{1.5mm} \\   
   	\textbf{Tinbergen Institute merit-based scholarship}\\ Tinbergen Institute, full scholarship, first and second year, 30,000 EUR \hfill Sep. 2013 -- Aug. 2015\vspace{1.5mm} \\   
       \textbf{Student Exchange Scholarship}\\  Warsaw School of Economics, the LLP Erasmus \hfill Sep. 2010 -- Feb. 2011\vspace{1.5mm} \\
       \textbf{Scholarship for excellent academic achievements}\\ Warsaw School of Economics \hfill Oct. 2007 -- Sep. 2010 

\newpage	

    % Computer Skills
   \section{\mysidestyle Computer\\ Skills} 
   Strong experience in MATLAB, Fortran, R   \vspace{1mm}\\
   Experience with Python, C, PHP, Visual Basic, SQL, BUGS/JAGS \vspace{1mm}\\
	Familiarity with EViews, Stata, SPSS \vspace{1mm} \\
 %   Databases:	EcoWin, Reuters \vspace{1mm}\\
	Other: \LaTeX, Linux, GitHub, SVN  

    % Foreign Languages
   \section{\mysidestyle Foreign Languages}  
	Polish (native), English (fluent),  German (advanced),    \\
    Russian (intermediate),  French (basic),  Dutch (basic)

 
    
\section{\mysidestyle Referees} 

 \textbf{Prof. Siem Jan Koopman} \\    
 The Department of Econometrics \\
 Vrije Universiteit Amsterdam, e-mail: \url{s.j.koopman@vu.nl}

 \textbf{Dr Lennart Hoogerheide} \\  
 The Department of Econometrics \\  
 Vrije Universiteit Amsterdam, e-mail: \url{l.f.hoogerheide@vu.nl}

 \textbf{Prof. Ruth King} \\  
 The School of Mathematics,\\  
 The University of Edinburgh, e-mail: \url{ruth.king@ed.ac.uk}
 
 \textbf{Prof. Herman K. van Dijk} \\  
 Econometric Institute,\\  
 Erasmus University Rotterdam, e-mail: \url{hkvandijk@ese.eur.nl }
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}